---
title: "Sugar in Fruits and Candies"
author: "Wenlong Yang"
date: "11/12/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Why sugar?

Sugar consumption is believed to be related to insulin resistance, and therefore all the western diseases (type ii diabetes, high blood pressure, heart attack, cancer, gout, etc.) 

There are different kinds of sugars. The fundamental ones are glucose, fructose and galactose. These are called monosaccharides or simple sugar. Disaccharide or double sugars are sugars that is composed of two simple sugars. For example, sucrose (table sugar) can be decomposed to glucose and fructose. Lactose can be decomposed to glucose and galactose. Maltose can be decomposed to two glucose. Glucose can be used as an energy source by almost every cell, while fructose and galactose are mostly metabolized in liver.

It is found that fructose is especially likely to cause insulin resistance. Since the table sugar is composed of one glucose and one fructose, eating a lot of table sugar can greatly increase the risk of insulin resistance and other western diseases.

This website showed the sugar content of 100 gram of fruits or candies.

<https://thepaleodiet.com/fruits-and-sugars/amp/>.

I analyzed the data and showed the results on a image

```{r data processing, include=FALSE}
library(rvest)
library(tidyverse)
url <- "https://thepaleodiet.com/fruits-and-sugars/amp/"
htmlsource <- read_html(url)
nodes <- html_nodes(htmlsource, "table")
fruit_sugar <- html_table(nodes[[1]])
names(fruit_sugar)[1] <- "Names"
fruit_sugar[is.na(fruit_sugar)]=0
write.csv(fruit_sugar,"Fruit_sugar_raw.csv")
row_freshfruit <- which(str_detect(fruit_sugar$Names,"FRESH FRUIT"))
row_dryfruit <- which(str_detect(fruit_sugar$Names,"DRIED FRUIT"))
row_pursugars <- which(str_detect(fruit_sugar$Names,"PURE SUGARS"))
row_candies <- which(str_detect(fruit_sugar$Names,"CANDY"))
fruit_sugar <- fruit_sugar %>% mutate(category="")
fruit_sugar$category[(row_freshfruit+1):(row_dryfruit-1)] <- "Fresh Fruit"
fruit_sugar$category[(row_dryfruit+1):(row_pursugars-1)] <- "Dried Fruit"
fruit_sugar$category[(row_pursugars+1):(row_candies-1)] <- "Pure Sugar"
fruit_sugar$category[(row_candies+1):nrow(fruit_sugar)] <- "Candies"
```


```{r data processing2, include=FALSE}
temp <- fruit_sugar%>% filter(category=="Candies") %>% mutate(`TOT. MET. FRUCTOSE`= if_else(`TOT. MET. FRUCTOSE`>`Total Sugars`/2, `TOT. MET. FRUCTOSE`,`Total Sugars`/2))

fruit_sugar[(row_candies+1):nrow(fruit_sugar),] <- temp

final_table <- fruit_sugar %>% mutate(Sugar_Percentage = `Total Sugars`/100, Fructose_Percentage = `TOT. MET. FRUCTOSE`/100, Fructose_per_Sugar=`TOT. MET. FRUCTOSE`/`Total Sugars`)
final_table <- na.omit(final_table)
write.csv(final_table,"fruit_candy_sugar.csv")
report_table <- final_table %>% select(Names,Sugar_Percentage,Fructose_per_Sugar,Fructose_Percentage,category)
write.csv(report_table,"report.csv")
```


You can also embed plots, for example:

```{r pressure, echo=FALSE}
report_table %>% ggplot(aes(Fructose_Percentage,reorder(Names,Fructose_Percentage),color=category)) + geom_point(size=1)+theme(axis.text.y=element_text(size=5), axis.title.y = element_blank())
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
